Score-based tests of measurement invariance: Use in practice

### 2013-09-05 frontiers/frontiers.Rnw
o Minor changes to frontiers manuscript o Added sim1 results file
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@249 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

if(file.exists("sim1.rda")) {
  load("sim1.rda")
} else {
  sim1 <- simulation(sim=c("sim1"), nobs=c(480),parms=c("loading","error","var"))
  sim1$nlevels <- factor(sim1$nlevels)
  levels(sim1$nlevels) <- paste("m=",levels(sim1$nlevels),sep="")
  sim1$nobs <- factor(sim1$nobs)
  levels(sim1$nobs) <- paste("n=",levels(sim1$nobs),sep="")
  levels(sim1$test) <- c("ordmax","ordwmax","catdiff")
  save(sim1, file="sim1.rda")
}
sim1$test <- factor(as.character(sim1$test),
  levels = c("ordmax","ordwmax","catdiff"),
  labels = c("ordmax","ordwmax","catdiff"))
@

@@

if(file.exists("sim2.rda")) {
  load("sim2.rda")
} else {
  sim2 <- simulation(sim=c("sim2"), nobs=c(480),parms=c("extra","extra+loading","extra+var","extra+error"))
  sim2$nlevels <- factor(sim2$nlevels)
  levels(sim2$nlevels) <- paste("m=",levels(sim2$nlevels),sep="")
  sim2$nobs <- factor(sim2$nobs)
  levels(sim2$nobs) <- paste("n=",levels(sim2$nobs),sep="")
  levels(sim2$test) <- c("ordmax","ordwmax","catdiff")
  save(sim2, file="sim2.rda")
}
sim2$test <- factor(as.character(sim2$test),
  levels = c("ordmax","ordwmax","catdiff"),
  labels = c("ordmax","ordwmax","catdiff"))
@

>>>>

if(file.exists("sim1.rda")) {
  load("sim1.rda")
} else {
  sim1 <- simulation(sim="sim1", nobs=480, parms=c("loading","error","var"))
  sim1$nlevels <- factor(sim1$nlevels)
  levels(sim1$nlevels) <- paste("m=",levels(sim1$nlevels),sep="")
  sim1$nobs <- factor(sim1$nobs)
  levels(sim1$nobs) <- paste("n=",levels(sim1$nobs),sep="")
  levels(sim1$test) <- c("ordmax","ordwmax","catdiff")
  save(sim1, file="sim1.rda")
}
sim1$test <- factor(as.character(sim1$test),
  levels = c("ordmax","ordwmax","catdiff"),
  labels = c("ordmax","ordwmax","catdiff"))
@

@@

if(file.exists("sim2.rda")) {
  load("sim2.rda")
} else {
  sim2 <- simulation(sim="sim2", nobs=480, parms=c("extra","extra+loading","extra+var","extra+error"))
  sim2$nlevels <- factor(sim2$nlevels)
  levels(sim2$nlevels) <- paste("m=",levels(sim2$nlevels),sep="")
  sim2$nobs <- factor(sim2$nobs)
  levels(sim2$nobs) <- paste("n=",levels(sim2$nobs),sep="")
  levels(sim2$test) <- c("ordmax","ordwmax","catdiff")
  save(sim2, file="sim2.rda")
}
sim2$test <- factor(as.character(sim2$test),
  levels = c("ordmax","ordwmax","catdiff"),
  labels = c("ordmax","ordwmax","catdiff"))
@
